Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-11-21 code/maps.qmd
Add site identifiers to Yosemite map

```{r}
translocation_points_map <- tm_shape(hillshade_yose_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(yose_boundary) + 
  tm_borders(col = "black", lwd = 2) +
  tm_shape(translocation_points) + 
  tm_symbols(size = 0.9, 
             shape = "donor_id",
             col = "type", 
             legend.shape.show = FALSE, 
             palette = c("#0000FF", "#C0FF3E"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Population type") +
  tm_layout(legend.position = c("right", "top"),
            legend.bg.color = "white",
            legend.title.size = 1.5,
            legend.text.size = 1.2) +
  tm_compass(type = "4star",
             position = c(0.80, 0.11),
             size = 5) +
  tm_scale_bar(breaks = c(0, 10, 20), 
               text.size = 1.2, 
               position = c("right", "bottom"))

>>>>

```{r}
translocation_points <- translocation_points %>% 
  mutate(
    label = case_when(
      site_id == 70567 ~ 4, 
      site_id == 72996 ~ 1
    ))

translocation_points_map <- tm_shape(hillshade_yose_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(yose_boundary) + 
  tm_borders(col = "black", lwd = 2) +
  tm_shape(translocation_points) + 
  tm_symbols(size = 3, 
             shape = "donor_id",
             col = "type", 
             legend.shape.show = FALSE, 
             palette = c("#0000FF", "#C0FF3E"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Population type") +
  tm_layout(legend.position = c("right", "top"),
            legend.bg.color = "white",
            legend.title.size = 1.5,
            legend.text.size = 1.2) +
  tm_text(text = "label") +
  tm_compass(type = "4star",
             position = c(0.80, 0.11),
             size = 5) +
  tm_scale_bar(breaks = c(0, 10, 20), 
               text.size = 1.2, 
               position = c("right", "bottom"))

### 2023-11-21 doc/manuscript/translocation.qmd
Add site identifiers to Yosemite map

---
bibliography: translocation.bib
csl: pnas.csl
# format: docx
format :
  latex:
    cite-method: natbib
editor: visual
editor_options:
  markdown:
    wrap: sentence
---

@@

![Map showing the locations of translocated and donor MYL frog populations in Yosemite National Park (park boundary indicated by black polygon). Symbol shapes indicate the donor population used for each translocation site. To obscure the exact locations of populations, random noise was added to all point coordinates. Inset map shows the location of Yosemite within California. In both maps, elevation is indicated by the colored hillshade layer (dark green = lowest elevation, white = highest elevation).](figures/map_translocation_points.png){#fig-yosemap width="250"}

>>>>

---
bibliography: translocation.bib
csl: pnas.csl
format: pdf
# format: docx
# format :
#  latex:
#    cite-method: natbib
editor: visual
editor_options:
  markdown:
    wrap: sentence
---

@@

![Map showing the locations of translocated and donor MYL frog populations in Yosemite National Park (park boundary indicated by black polygon). Symbol shapes indicate the donor population used for each translocation site, and numbers inside the donor symbols refer to sites identified in @fig-allelefrequencies. To obscure the exact locations of populations, random noise was added to all point coordinates. Inset map shows the location of Yosemite within California. In both maps, elevation is indicated by the colored hillshade layer (dark green = lowest elevation, white = highest elevation).](figures/map_translocation_points.png){#fig-yosemap width="400"}
